Figure 2 and figure 2 supplementary material

### 2022-03-09 Figures/Figure2.Rmd
add to wrapper_tpurity choose estimate

################################################################################
wrapper_tpurity <- function(deconv_data, true_estimates, cancer_abreviation){
  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_

@@

  final_plot = list()
  color = "black"
  x_lab = "ESTIMATE"

  title = "ESTIMATE vs CCLE TIL10 Cancer"
  y_lab = "CCLE TIL10 Cancer"
  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)

  # Scatterplot BPRNACan
  title = "ESTIMATE vs BPRNACan Cancer"
  y_lab = "BPRNACan Cancer"
  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, "ESTIMATE", "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)

@@

# Figure
## A) Tumor Purity
```{r}
wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = , cancer_abreviation = "LUAD")
```

@@

for (cancer in unique(HE_all_TCGA$Study)){
  ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
  tpurity_by_cancer[[cancer]] <- tryCatch({ wrapper_tpurity(deconv_data = tcga_deconv, true_estimates = Aran_all_facs, cancer_abreviation = cancer) # sometimes there arent enough samples of the tumour type
        },
        error = function(cond) {
          message(paste("not enough FACs samples for ", cancer, "no scatterplot will be generated"))
          return(list(ccle = blank, bprna = blank))
        }
  )
  tpurity_by_cancer[[cancer]]$extra = blank

>>>>

################################################################################
wrapper_tpurity <- function(deconv_data, true_estimates, estimate, cancer_abreviation){
  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_

@@

  final_plot = list()
  color = "black"
  x_lab = estimate

  title = paste0(estimate, " vs CCLE TIL10 Cancer")
  y_lab = "CCLE TIL10 Cancer"
  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)

  # Scatterplot BPRNACan
  title = paste0(estimate, " vs BPRNACan Cancer")
  y_lab = "BPRNACan Cancer"
  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)

@@

# Figure
## A) Tumor Purity
```{r}
wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = "ABSOLUTE" , cancer_abreviation = "LUAD")
```

@@

for (cancer in unique(HE_all_TCGA$Study)){
  ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
  tpurity_by_cancer[[cancer]] <- tryCatch({ wrapper_tpurity(deconv_data = tcga_deconv, true_estimates = Aran_all_facs, estimate = "ABSOLUTE", cancer_abreviation = cancer) # sometimes there arent enough samples of the tumour type
        },
        error = function(cond) {
          message(paste("not enough FACs samples for ", cancer, "no scatterplot will be generated"))
          return(list(ccle = blank, bprna = blank))
        }
  )
  tpurity_by_cancer[[cancer]]$extra = blank
